---
title: "Activity: Nuclear Reactors"
author: "Jai abhishek singh"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)

```

## Scrape the Data 

```{r}
# Define the URL for Wikipedia page
url <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"

# Read content from html page
page <- read_html(url)

# Extract tables on the page
tables <- page %>%
  html_nodes("table") %>%
  html_table(fill = TRUE)

# Check the number of tables found
length(tables)

# Extract Japan's reactor
japan_table_index <-   # Check and adjust the index as necessary
japan_reactors_raw <- tables[[japan_table_index]]

# Display the head of the raw table to verify
head(japan_reactors_raw)


```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

For a tidy table , Each variable should have its own column , Each observation should be in its own row , Each type of observational unit should form a table.


The table has a structured format with columns representing different attributes of nuclear reactors, such as "Name," "Unit No.," and "Type."

The table has duplicate columns with similar names, such as  "Capacity (MW)."


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
japan_reactors_clean <- japan_reactors_raw %>%
  rename(
    Name = `Plantname`,
    UnitNo = `UnitNo.`,
    ReactorType = `Type`,
    ReactorModel = `Model`,
    Status = `Status`,
    NetMW = `Capacity(MW)`,
    GrossMW = `Capacity(MW)`,
    ConstructionStart = `Beginbuilding`,
    CommercialOperation = `Commercialoperation`,
    Closure = `Closed`
)

# Display the cleaned data
head(japan_reactors_clean)

# Plot Net Generation Capacity vs Construction Date
ggplot(japan_reactors_clean, aes(x = ConstructionStart, y = GrossMW, color = ReactorType)) +
  geom_point() +
  labs(
    title = "Net Generation Capacity vs. Construction Date (Japan Reactors)",
    x = "Construction Start Date",
    y = "Net Capacity (MW)"
  ) +
  theme_minimal() +
  scale_color_brewer(palette = "Set2")



```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}


china_table_index <- 
china_reactors_raw <- tables[[china_table_index]]

# Display the cleaned data

head(japan_reactors_clean)

head(china_reactors_raw)

# Clean and tidy China's reactor data
china_reactors_clean <- china_reactors_raw 

# Add country column for both datasets
japan_reactors_clean <- japan_reactors_clean %>% mutate(Country = "Japan")
china_reactors_clean <- china_reactors_clean %>% mutate(Country = "China")

# Merge the datasets
reactors_combined <- bind_rows(japan_reactors_clean, china_reactors_clean)

# Display the combined data
head(reactors_combined)


```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}

ggplot(japan_reactors_clean, aes(y = Name)) +
  geom_segment(aes(x = ConstructionStart, xend = CommercialOperation, yend = Name), color = "blue") +
  geom_point(aes(x = ConstructionStart), color = "red", size = 3) +
  geom_point(aes(x = CommercialOperation), color = "green", size = 3) +
  labs(
    title = "Construction to Operation Timeline of Japan's Nuclear Reactors",
    x = "Date",
    y = "Reactor Name"
  ) +
  theme_minimal() 

```
